### 2012-10-02 doc/prelim/document/chapters/introduction/introduction.tex
grammar fix in intro

\section{Hardware-Based Motivation}
\label{sec:hardware_motivation}
As leadership class machines move towards the exascale, new algorithms
must developed that leverage their strengths and adapt to their
shortcomings. Basic research is required now to advance methods in
time for these new machines to become operational. Organized work is
already moving forward in this area with the Department of Energy's
Advanced Scientific Computing Research office specifically allocating
funding for the next several years to research resilient solver
technologies for exascale facilities
\citep{u.s._department_of_energy_resilient_2012}. Based on the
language in this call for proposals, we can identify key issues that a
set of robust, massively parallel stochastic solvers could provide a
solution for. As machines begin to operate at hundreds of petaflops
peak performance and beyond, restrictions on power availability will
require incredibly high levels of concurrency. Furthermore, this drop
in power consumption will mean increased pressure on memory as memory
per node is expected to stagnate while cores per node is expected to
increase. As the number of cores increases, their clock speed is
expected to stagnate or even decrease to further reduce power
consumption and manufacturing costs.

>>>>

\section{Hardware-Based Motivation}
\label{sec:hardware_motivation}
As leadership class machines move towards the exascale, new algorithms
must developed that leverage their strengths and adapt to their
shortcomings. Basic research is required now to advance methods in
time for these new machines to become operational. Organized work is
already moving forward in this area with the Department of Energy's
Advanced Scientific Computing Research office specifically allocating
funding for the next several years to research resilient solver
technologies for exascale facilities
\citep{u.s._department_of_energy_resilient_2012}. Based on the
language in this call for proposals, we can identify key issues for
which a set of robust, massively parallel stochastic solvers could
provide a solution. As machines begin to operate at hundreds of
petaflops peak performance and beyond, restrictions on power
availability will require incredibly high levels of
concurrency. Furthermore, this drop in power consumption will mean
increased pressure on memory as memory per node is expected to
stagnate while cores per node is expected to increase. As the number
of cores increases, their clock speed is expected to stagnate or even
decrease to further reduce power consumption and manufacturing costs.
